Toxic Code Snippets on Stack Overflow

### 2018-11-24 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Updated the authors' affiliations in the response letter and completed the cross-check that all the changes in the response letter have been applied to the paper. Start proofreading the paper.

% 2. Complete the paper data
\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$,~Jens Krinke$^\dagger$,~Matheus Paixao$^\dagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
\newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
%\newcommand{\myEmail}{cragkhit@gmail.com, {j.krinke,matheus.paixao.14}@ucl.ac.uk, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
%\newcommand{\mySecEmail}{}
\newcommand{\myTitle}{Cover Letter for the Reviewers of the Paper \\ ``Toxic Code Snippets on Stack Overflow''}
\newcommand{\myShortTitle}{Cover Letter}
\newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, University of Molise (Italy)$^\star$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{center}
 {\LARGE\myTitle} \vspace{0.3cm} \\
 {\large\myJournal} \vspace{0.3cm} \\
 \today \vspace{0.3cm} \\
 \myAuthors \\
% \url{\myEmail} \\
 %\url{\mySecEmail} 
 \vspace{0.3cm} 
 \myDept \vspace{1cm}
\end{center}

@@

\rcomment{The paper presents an interesting empirical analysis of what the authors refers to as toxic code clones on Stack Overflow. The paper presents a study using state-of the art clone detection tools and techniques to automatically extract and filter online clone pairs between Stack Overflow and projects in the curated Qualitas corpus. The paper also includes a user survey conducted on Stack Overflow users to assess their awareness of such potential toxic code fragments.he paper is well organized,  sound and the authors spend amount of work in their empirical analysis.
\vspace{0.2cm}

@@

Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of (only) 111 Java projects from the Qualitas corpus. The clones (and the discovered outdated code and potentially license-violating code snippets) reported in this paper are only subject to these 111 projects. The number may increase if we expand the amount of open source projects. Moreover, this study only focuses on Java, and the situation may be worse or better for other programming languages. We have added this discussion into the Threats to Validity. \FIXME{Done}

@@

We have added this discussion in the Threats to Validity section \FIXME{Done}.

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and were fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer \FIXME{Done}.

@@

Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{Done}.

\rcomment{R2C8: Thank you for clarifying the manual analysis part. Can please provide more details on how this manual analysis determined that something actually originated from SO? Perhaps giving an example would help here. Also, who did this verification?}

In the case of cloning direction from Stack Overflow $\rightarrow$ Qualitas
(SQ), we found only one pair with evidence of cloning from Stack Overflow post
ID 698283 to {\small\texttt{POIUtils.java}} in the \textsf{jstock} project (as shown below). 
The Stack Overflow post can be seen at \url{https://stackoverflow.com/questions/698176/determine-correct-method-signature-during-runtime/698283#698283}.
The user who asked the question (i.e., Cheok Yan Cheng) on Stack Overflow is an author of \textsf{jstock} (the author's GitHub profile can be seen from \url{https://github.com/yccheok}). The
question is about determining the right method to call among 7 overloading
methods of {\small\texttt{setCellValue}} during runtime. We could not find
evidence of copying or attribution to Stack Overflow in \textsf{jstock}.
However, considering that the 25 lines of code of
{\small\texttt{findMethodToInvoke}} method depicted in  in Stack Overflow is
very similar to the code in \textsf{jstock} including comments, it is almost
certain that the two code snippets form a clone pair. In addition, the Stack
Overflow answer was posted on March 30, 2009, while the code in
{\small\texttt{POIUtils}} class in \textsf{jstock} was committed to GitHub on
the next day of March 31, 2009. 
The git blame of the file \texttt{POIUtils.java} 
containing the clone can be found from \url{https://github.com/yccheok/jstock/blame/master/src/org/yccheok/jstock/gui/POIUtils.java} (line 99--123).

@@

``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{Done}

@@

Again, we agree with your suggestion. The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''. \FIXME{Done}

>>>>

% 2. Complete the paper data
\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while the first and the third author were PhD students at CREST, University College London},~Jens Krinke$^\dagger$,~Matheus Paixao$^\ddagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
\newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
\newcommand{\myEmail}{chaiyong.rag@mahidol.ac.th, j.krinke@ucl.ac.uk, matheus.paixao@uece.br, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
%\newcommand{\mySecEmail}{}
\newcommand{\myTitle}{Cover Letter for the Reviewers of the Paper \\ ``Toxic Code Snippets on Stack Overflow''}
\newcommand{\myShortTitle}{Cover Letter}
\newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, 
	State University of Ceara (Brazil)$^\ddagger$,
	University of Molise (Italy)$^\star$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{center}
 {\LARGE\myTitle} \vspace{0.3cm} \\
 {\large\myJournal} \vspace{0.3cm} \\
 \today \vspace{0.3cm} \\
 \myAuthors \\
 \url{\myEmail} \\
 %\url{\mySecEmail} 
 \vspace{0.3cm} 
 \myDept \vspace{1cm}
\end{center}

@@

\rcomment{The paper presents an interesting empirical analysis of what the authors refers to as toxic code clones on Stack Overflow. The paper presents a study using state-of the art clone detection tools and techniques to automatically extract and filter online clone pairs between Stack Overflow and projects in the curated Qualitas corpus. The paper also includes a user survey conducted on Stack Overflow users to assess their awareness of such potential toxic code fragments. The paper is well organized, sound and the authors spend amount of work in their empirical analysis.
\vspace{0.2cm}

@@

Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of (only) 111 Java projects from the Qualitas corpus. The clones (and the discovered outdated code and potentially license-violating code snippets) reported in this paper are only subject to these 111 projects. The number may increase if we expand the amount of open source projects. Moreover, this study only focuses on Java, and the situation may be worse or better for other programming languages. We have added this discussion into the Threats to Validity.

@@

We have added this discussion in the Threats to Validity section.

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and were fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer.

@@

Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section.

\rcomment{R2C8: Thank you for clarifying the manual analysis part. Can you please provide more details on how this manual analysis determined that something actually originated from SO? Perhaps giving an example would help here. Also, who did this verification?}

In the case of cloning direction from Stack Overflow $\rightarrow$ Qualitas
(SQ), we found only one pair with evidence of cloning from Stack Overflow post
ID 698283 to {\small\texttt{POIUtils.java}} in the \textsf{jstock} project (as shown below). 
The Stack Overflow post can be seen at \url{https://stackoverflow.com/questions/698176/determine-correct-method-signature-during-runtime/698283#698283}.
The user who asked the question (i.e., Cheok Yan Cheng) on Stack Overflow is an author of \textsf{jstock} (the author's GitHub profile can be seen from \url{https://github.com/yccheok}). The
question is about determining the right method to call among 7 overloading
methods of {\small\texttt{setCellValue}} during runtime. We could not find
evidence of copying or attribution to Stack Overflow in \textsf{jstock}.
However, considering that the 25 lines of code of
{\small\texttt{findMethodToInvoke}} method (depicted in Figure \ref{fig:jstock_code} below) on Stack Overflow is
very similar to the code in \textsf{jstock} including comments, it is almost
certain that the two code snippets form a clone pair. In addition, the Stack
Overflow answer was posted on March 30, 2009, while the code in
{\small\texttt{POIUtils}} class in \textsf{jstock} was committed to GitHub on
the next day of March 31, 2009. 
The git blame of the file \texttt{POIUtils.java} 
containing the clone can be found from \url{https://github.com/yccheok/jstock/blame/master/src/org/yccheok/jstock/gui/POIUtils.java} (line 99--123).

@@

``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}''

@@

Again, we agree with your suggestion. The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''.
